Effective collector efficiency of sparse and dense arrays of emergent cylindrical collectors in laminar-turbulent transitional flows

### 2020-10-21 aa workingdraft/draft.tex
almost done with parameter table

\begin{table}[H]
\caption{Experimental and natural parameter ranges. Natural values are approximations based on field observations \cite{Nepf_2012}.}
\centering
%% \tablesize{} %% You can specify the fontsize here, e.g., \tablesize{\footnotesize}. If commented out \small will be used.
\begin{tabular}{lcccc}
\toprule
\textbf{Parameter}&\textbf{This study}&\textbf{Fauria et al. (2015)}&\textbf{Purich (2006)}&\textbf{Natural}\\
\midrule
Flow velocity (\SI{}{\centi\metre/\second})     & 2.0--6.0 & 1.8--6.1 & 1.0--10.2 & 0--25     \\
Flow depth (\SI{}{\centi\metre})                & 40       & 14--17   & 12        & 0--50     \\
Average collector diameter (\SI{}{\centi\metre})& 0.318    & 0.3      & 0.63      & 0.1--1    \\

>>>>

\begin{table}[H]
\caption{Experimental and natural parameter ranges. Natural values are approximations from other studies \cite{Nepf_2012,kadlec1990, czuba2015sedgravity}. Asterisk marks where empirical estimates \cite{mckenzie2008size} replace missing study-specific data.}
\centering
%% \tablesize{} %% You can specify the fontsize here, e.g., \tablesize{\footnotesize}. If commented out \small will be used.
\begin{tabular}{lcccc}
\toprule
\textbf{Parameter}&\textbf{This study}&\textbf{Fauria et al. (2015)}&\textbf{Purich (2006)}&\textbf{Natural}\\
\midrule
Flow velocity (\SI{}{\centi\metre/\second})     
& 2.0--6.0    & 1.8--6.1    & 1.0--10.2    & 0--25     \\
Flow depth (\SI{}{\centi\metre})                
& 40          & 14--17      & 12           & 0--50     \\
\midrule
%Collector type
%& greased cylinders & artificial leaves  & greased cylinders & e.g., stems, leaves \\ 
Collector diameter (\SI{}{\centi\metre})
& 0.318       & 0.3         & 0.63         & 0.1--1    \\
Collector Reynolds number                       
& 66--200     & 54--183     & 70--640      & 5--1000   \\ 
Collector density ($\#/m^2$)&&&&\\

Frontal area density, $a$ (\SI{}{\per\meter})&&&&\\

Solid volume fraction, $\phi_c$ &&&&\\

\midrule
%Particle type
%& ground walnut shell  & road dust  & Pliolite    & e.g., silt, clay \\ 
Specific gravity      
& 1.53        &2.27--2.61*  & 1.03        & 2.56--2.87   \\
Particle diameter (\SI{}{\micro\metre})     
& 1.53        &1.25--250  & 212--250        &    \\
Suspended concentration (\SI{}{\micro\liter/\liter})      
&   &   &    &    \\
\midrule
Particle-collector diameter ratio, $R$      
&   &   &    &    \\
